Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
renew Fig 5 + caption

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/supervised_rbf_test3.eps}
\caption{... \ja{What is this?}}
\end{center}
\end{figure}

@@

MFCC \vs scattering

Object-based \vs early/late integration

Role of logarithmic compression

\vl{Results: DCASE 2016}

@@

Representign a scene using a reduced set of exemplars, in the form of centroids, with adapted similarity strategies allows us to improve ASSR performance compared to the insufficient BOF approaches based on GMMs. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

>>>>

\subsubsection*{MFCCs \vs scattering}
As shown in Figure, log-scattering coefficients consistently outperform $MFCCs$ over all folds of the DCASE 2013 private dataset.
The average accuracy

\subsubsection*{Early \vs late integration}

\subsubsection*{Participation to the DCASE 2016 challenge}
In order to evaluate how general these results are, we have taken part in the acoustic scene classification task 2016 edition of the DCASE challenge.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) with a Gaussian radial kernel.
See text for details.}
\end{center}
\ref{fig:folds}
\end{figure}

@@

@@

Representing a scene using a reduced set of exemplars, in the form of centroids, with adapted similarity strategies allows us to improve ASSR performance compared to the insufficient BOF approaches based on GMMs. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- are represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}
